working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-03-10 Manuscript_draft/Manuscript_draft.Rmd
edits

Results of hand cross-pollination, hand self-pollination, natural selfing and apomixis are presented in **Figure 1** (see appendix 1 for table with values). Heterospecific pollen reduced seed set significatively with the 50-50% heterospecific pollen treatments for 65% of the pairwise interactions p<0.05. Moreover, average effect sizes differed across species and across families, see **Figure 2**. Despite some variability in the effect of the different pollen donors per species, in general terms the effect of heterospecific pollen from the distinct nine treatments per species was homogeneous (see **Figure 3**), just for four species out of ten, just one donor did not overlap the confidence intervals with other donors. Therefore, none of the donors had a clear stronger or weaker effect across species. When the donors were groped by family not big differences were seen, just for *S. lycopersicum* the confidence intervals of Brassicaceae and Convolvulaceae did not overlap. In addition,

Now talk about the 100%, Make plot!!!!

 The 100% foreign pollen treatments barely produced seeds or fruits [and just for *Sinapis alba* we did not find significant differences between the hand cross-pollination and one treatment with pollen from a confamilial- IB Unclear](). Solanaceae species with berry fruit type developed small fruits or even normal fruits in some cases [under which treatment](). *S. lycopersicum* seems to produced small fruits (35% of the treatments) independently of pollen and pollen donor due to also apomictic treatments did, never normal size. *C. annuum* produced some fruits (9%) of both small and normal size and finally *S. melongena* produced seedless normal fruits with just confamilial pollen (3%), for both species seems that fruit formation was induced by pollen on the stigma because of lack of fruit production with treatments that tested for apomixis.[clarify this descriptive statistics part- Also a figure with a summary of the treatments effect would be cool, or at least in the appendices]()

>>>>

Results of hand cross-pollination, hand self-pollination, natural selfing and apomixis are presented in **Figure 1** (see appendix 1 for table with values). Heterospecific pollen reduced seed set significatively with the 50-50% heterospecific pollen treatments for 65% of the pairwise interactions p<0.05. Moreover, average effect sizes differed across species and across families, see **Figure 2**. Despite some variability in the effect of the different pollen donors per species, in general terms the effect of heterospecific pollen from the distinct nine treatments per species was homogeneous (see **Figure 3**), just for four species out of ten, just one donor did not overlap the confidence intervals with other donors. Therefore, none of the donors had a clear stronger or weaker effect across species. When the donors were groped by family not big differences were seen, just for *S. lycopersicum* the confidence intervals of Brassicaceae and Convolvulaceae did not overlap (see **Figure 4**). In addition, for the 100% hetrospecific pollen treatments we did not find almost seed production. However, for just one species (*S. alba*) the control pollination and the heterospecific pollination with pollen from a confamilial had similar seed production. For both Solanaceae species *S. melongena* and *C. annuum* 100% pollen treatments produced few seedles fruits (3% and 9% respectively) and they did not for the apomictic treatments.

### 2019-03-10 Manuscript_draft/Manuscript_draft.tex
edits

Results of hand cross-pollination, hand self-pollination, natural
selfing and apomixis are presented in \textbf{Figure 1} (see appendix 1
for table with values). Heterospecific pollen reduced seed set
significatively with the 50-50\% heterospecific pollen treatments for
65\% of the pairwise interactions p\textless{}0.05. Moreover, average
effect sizes differed across species and across families, see
\textbf{Figure 2}. Despite some variability in the effect of the
different pollen donors per species, in general terms the effect of
heterospecific pollen from the distinct nine treatments per species was
homogeneous (see \textbf{Figure 3}), just for four species out of ten,
just one donor did not overlap the confidence intervals with other
donors. Therefore, none of the donors had a clear stronger or weaker
effect across species. When the donors were groped by family not big
differences were seen, just for \emph{S. lycopersicum} the confidence
intervals of Brassicaceae and Convolvulaceae did not overlap. In
addition,

Now talk about the 100\%, Make plot!!!!

The 100\% foreign pollen treatments barely produced seeds or fruits
\href{}{and just for \emph{Sinapis alba} we did not find significant
differences between the hand cross-pollination and one treatment with
pollen from a confamilial- IB Unclear}. Solanaceae species with berry
fruit type developed small fruits or even normal fruits in some cases
\href{}{under which treatment}. \emph{S. lycopersicum} seems to produced
small fruits (35\% of the treatments) independently of pollen and pollen
donor due to also apomictic treatments did, never normal size. \emph{C.
annuum} produced some fruits (9\%) of both small and normal size and
finally \emph{S. melongena} produced seedless normal fruits with just
confamilial pollen (3\%), for both species seems that fruit formation
was induced by pollen on the stigma because of lack of fruit production
with treatments that tested for apomixis.\href{}{clarify this
descriptive statistics part- Also a figure with a summary of the
treatments effect would be cool, or at least in the appendices}

>>>>

Results of hand cross-pollination, hand self-pollination, natural
selfing and apomixis are presented in \textbf{Figure 1} (see appendix 1
for table with values). Heterospecific pollen reduced seed set
significatively with the 50-50\% heterospecific pollen treatments for
65\% of the pairwise interactions p\textless{}0.05. Moreover, average
effect sizes differed across species and across families, see
\textbf{Figure 2}. Despite some variability in the effect of the
different pollen donors per species, in general terms the effect of
heterospecific pollen from the distinct nine treatments per species was
homogeneous (see \textbf{Figure 3}), just for four species out of ten,
just one donor did not overlap the confidence intervals with other
donors. Therefore, none of the donors had a clear stronger or weaker
effect across species. When the donors were groped by family not big
differences were seen, just for \emph{S. lycopersicum} the confidence
intervals of Brassicaceae and Convolvulaceae did not overlap (see
\textbf{Figure 4}). In addition, for the 100\% hetrospecific pollen
treatments we did not find almost seed production. However, for just one
species (\emph{S. alba}) the control pollination and the heterospecific
pollination with pollen from a confamilial had similar seed production.
For both Solanaceae species \emph{S. melongena} and \emph{C. annuum}
100\% pollen treatments produced few seedles fruits (3\% and 9\%
respectively) and they did not for the apomictic treatments.
